LAI workflow

### 2021-01-20 LAI.Rmd
Language correction

2. Restricted leaf-litter data to the last 7 years for BCI-Poachers and BCI-50ha, converted observed leaf fall data column in mass units (leaf_gm) to mass per unit ground area as follows:  
    Leaf in gm per m2 ground area at a site = Leaf biomass in gm / (Site-specific trap area in m2  x Number of leaves were collected from) --- (Eq 1)  
    In Joe's the dataframe, column "leaf_gm"" represents leaf~biomass~in~gm and column "n_traps" represents the number of traps the leaf_gm observation came from.

>>>>

2. Restricted leaf-litter data to the last 7 years for BCI-Poachers and BCI-50ha, converted observed leaf fall data column in mass units (leaf_gm) to mass per unit ground area as follows:  
    Leaf in gm per m2 ground area at a site = Leaf biomass in gm / (Site-specific trap area in m2  x Number of traps leaves were collected from) --- (Eq 1)  
    In Joe's the dataframe, column "leaf_gm"" represents leaf~biomass~in~gm and column "n_traps" represents the number of traps the leaf_gm observation came from.
